### 2020-04-02 draft_ABP.tex
Update draft_ABP.tex

Generally, we can consider an arbitrary set of subsets of $[0,n]$ in eq.\eqref{stringyintforgenpermutohedron}. 
However, the big polytope for such integral in general is not a simplex.
It's highly non-trivial to figure out all such sets whose big polytopes are simplices,
but we can easily see that every generalized permutahedron satisfies $N=n+m$
because each facet $F_I$ is given by a nested set $\{[0,n],I\}$ for $I\neq [0,n]$.
Therefore, for a generalized permutahedron $\mathscr P$, we can write down the matrix 
$W^J_A$ of facets and then get the ABHY conditions $S_J=F_A(W^{-1})^A_J\geq 0$ and 
its $u$-variables $u_A=\prod_J p_J^{(W^{-1})^A_J}$.

Let's first write down equations of facets of a generalised permutahedron
with the building set $\mathscr P$. The ABHY polytope of 
eq.\eqref{stringyintforgenpermutohedron} is given by the Minkowski sum
\[
	- \sum_{I\in\mathscr P,|I|>1}S_I.\Delta_I
\]
in $(S_0,\dots,S_n)$-space, where $\Delta_I=\operatorname{ConvexHull}
(\{e_i\}_{i\in I})$. Meanwhile, we know from the last subsection that the facet 
labeled by a nested set $\{[0,n],I\}$ is given by
\begin{align*}
	\biggl\{(S_0,S_1,\dots,S_n)\in \mathbb R^{n+1}\,\bigg |\,
		\sum_{i\in I}S_i = -\sum_{J\subset I,|J|>1,J\in \mathscr P}S_J,
		\quad
		&\sum_{i=0}^nS_i=-\sum_{J\in \mathscr P,|J|>1}S_J,\\
		&\sum_{i\in K}S_i\geq -\sum_{J\subset I,|J|>1,J\in \mathscr P}S_J
	\biggr\},
\end{align*}
where the second constrain is just $\sum_{I\in \mathscr P}S_I=0$, so the equation 
of this facet is 
\begin{equation}\label{GPfacet}
	F_I:=\sum_{J\subset I,J\in\mathscr P}S_J=0.
\end{equation}

@@

@@

(Zhenjie: A possible way to find some $u$-equations of generalized permutohedra:)

For a generic generalized permutohedra $\mathscr P$, it's usually difficult to solve $S_I$ by $\{F_I\}$  from eq.\eqref{GPfacet} and then get $u$-variables, but we can directly use eq.\eqref{GPfacet} to express $x_I$ by $\{u_I\}$ which give us many algebraic equations of $u$-variables. In fact,
\[
\prod_{I\in \mathscr P}x_I^{S_I}=\prod_{J\in \mathscr P}u_J^{F_J}=\prod_{J\in\mathscr P}\prod_{I\subset J,I\in \mathscr P}u_J^{S_I}=\prod_{I\in\mathscr P}\biggl(\prod_{J\supset I,J\in\mathscr P}u_J\bigg)^{S_I},
\]
so
\[
x_I=\prod_{J\supset I,J\in\mathscr P}u_J
\]
for any $I\in \mathscr P$, where we introduce a fake $u$-variable $u_{[0,n]}:=x_{[0,n]}$. We know some algebraic equations of $\{x_I\}$, for example, $x_I+x_J=x_{[0,n]}$ for $I\cap J=\varnothing$ and $I\cup J=[0,n]$, so (I will omit all $\text{sth}\in \mathscr P$ for short.)
\[
\prod_{K\supset I}u_K+\prod_{K\supset J}u_K=u_{[0,n]},
\]
or (since we always assume that $u_{[0,n]}=x_{[0,n]}\neq 0$)
\[
\prod_{I\subset K\neq [0,n]}u_K +
\prod_{J\subset K\neq [0,n]}u_K = 1.
\]
(Zhenjie: I guess all possible $u$-equations are consequences of some algebraic equations of $x_I$ which is in fact we have seen in the calculation of $1-u_I$.)

% This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.

>>>>

Generally, we can consider an arbitrary set of subsets of $[0,n]$ in eq.\eqref{stringyintforgenpermutohedron}. 
However, the big polytope for such integral in general is not a simplex.
It's highly non-trivial to figure out all such sets whose big polytopes are simplices,
but we can easily see that every generalized permutahedron satisfies $N=n+m$
because each facet $F_I$ is given by a nested set $\{[0,n],I\}$ for $I\neq [0,n]$.
Therefore, for a generalized permutahedron $\mathscr P$, we can write down the matrix 
$W^J_A$ of facets and then get $S_J=F_A(W^{-1})^A_J\geq 0$ and 
its $u$-variables $u_A=\prod_J p_J^{(W^{-1})^A_J}$.

Let's first write down equations of facets of a generalised permutahedron
with the building set $\mathscr P$. The polytope of 
eq.\eqref{stringyintforgenpermutohedron} is given by the Minkowski sum
\[
	- \sum_{I\in\mathscr P,|I|>1}S_I.\Delta_I
\]
in $(S_0,\dots,S_n)$-space, where $\Delta_I=\operatorname{ConvexHull}
(\{e_i\}_{i\in I})$. Meanwhile, we know from the last subsection that the facet 
labeled by a nested set $\{[0,n],I\}$ is given by
\begin{align*}
	\biggl\{(S_0,S_1,\dots,S_n)\in \mathbb R^{n+1}\,\bigg |\,
		\sum_{i\in I}S_i = -\sum_{J\subset I,|J|>1,J\in \mathscr P}S_J,
		\quad
		&\sum_{i=0}^nS_i=-\sum_{J\in \mathscr P,|J|>1}S_J,\\
		&\sum_{i\in K}S_i\geq -\sum_{J\subset I,|J|>1,J\in \mathscr P}S_J
	\biggr\},
\end{align*}
where the second constrain is just $\sum_{I\in \mathscr P}S_I=0$, so the equation 
of this facet is 
\begin{equation}\label{GPfacet}
	F_I:=\sum_{J\subset I,J\in\mathscr P}S_J=0.
\end{equation}

@@

For permutahedra, we can give a ABHY construction from eq.\eqref{SinF} by setting 
$S_I=-c_I$ for any non-singleton $I\in \mathscr P_n$, where $c_I$ are positive 
constants, and a ABHY polytope is given by 
\begin{equation}\label{ABHY}
	F_I\geq 0,\quad -c_I=\sum_{J\neq \varnothing,J\subset I}(-1)^{|J|-|I|}F_J
\end{equation}
in $\{S_i=F_i\,:\,1\leq i\leq n\}$-space, where the last equation is a gauge fixing. 
According to eq.\eqref{genperm_defi}, this polytope is a $n$-dimensional 
permutahedron $\mathscr P_n$. {\bf (???)}
The ABHY construction of any generalized permutohedra can be obtained by 
setting $c_I=0$ for all $I$ not in the building set.

For example, the building set of $\mathscr A_2$ is $\mathscr P_2-\{\{0,2\}\}$,
its ABHY construction can be obtained from $\mathscr P_2$ by setting $c_{02}=0$, 
\[
	0=-c_{02}=F_{02}-F_2,
\]
therefore the whole ABHY conditions for $\mathscr A_2$ is 
\[
	-c_{01}=F_{01}-F_0-F_1,\quad -c_{12}=F_{12}-F_1-F_2,\quad 
	-c_{012}=-F_{01}-F_{12}+F_1,\quad F_I\geq 0,
\]
and its solution in $(F_1,F_2)$ space is 
\[
	\left\{\begin{aligned}
		F_1&\geq 0,F_2\geq 0\\
		F_0&=c_{01}+c_{12}+c_{012}-F_1-F_2\geq 0,\\
		F_{12}&=F_1+F_2-c_{12}\geq 0,\\
		F_{01}&=c_{012}+c_{12}-F_2\geq 0.
	\end{aligned}\right.
\]

@@

({\bf Zhenjie}: A possible way to find some $u$-equations of generalized permutohedra)

For a generic generalized permutohedra $\mathscr P$, it's usually difficult to solve $S_I$ by $\{F_I\}$  from eq.\eqref{GPfacet} and then get $u$-variables, but we can directly use eq.\eqref{GPfacet} to express $x_I$ by $\{u_I\}$ which give us many algebraic equations of $u$-variables. In fact,
\[
\prod_{I\in \mathscr P}x_I^{S_I}=\prod_{J\in \mathscr P}u_J^{F_J}=\prod_{J\in\mathscr P}\prod_{I\subset J,I\in \mathscr P}u_J^{S_I}=\prod_{I\in\mathscr P}\biggl(\prod_{J\supset I,J\in\mathscr P}u_J\bigg)^{S_I},
\]
so
\[
x_I=\prod_{J\supset I,J\in\mathscr P}u_J
\]
for any $I\in \mathscr P$, where we introduce a fake $u$-variable 
$u_{[0,n]}:=x_{[0,n]}$. We know some algebraic equations of $\{x_I\}$, 
for example, linear equations $x_I+x_J=x_{I\cup J}$ for $I\cap J=\varnothing$, 
so (I will omit all $\text{sth}\in \mathscr P$ for short.)
\begin{equation*}
	\prod_{K\supset I}u_K+\prod_{K\supset J}u_K=\prod_{K\supset I\cup J}u_K
\end{equation*}
or equivalently
\begin{equation}
\prod_{I\subset K,K\not\supset I\cup J}u_K +
\prod_{J\subset K,K\not\supset I\cup J}u_K = 1.
\end{equation}
({\bf Zhenjie}: I conjecture that all possible $u$-equations are consequences of 
some algebraic equations of $x_I$ which is in fact we have seen in 
the calculation of $1-u_I$. For example, the nonlinear equation (although it's
the consequence of linear equations)
\[
	x_0x_{012}+x_1x_2=x_{01}x_{02}
\]
tell us the $u$-equation of $u_0$ of 2d permutohedron $\mathscr P_2$. Therefore,
another related conjecture is that the variety generated by $u$-equations 
is the one generated by eq.(\theequation) for all disjoint $I$, $J\in \mathscr P$ 
in $u$-space. Can we prove that generalized permutohedra are binary geometries in
this way?
)
% This conjecture can be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
